\documentclass[paper=letter, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size

\usepackage{enumitem}
\usepackage{listings,multicol}
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
\usepackage[english]{babel} % English language/hyphenation
\usepackage{amsmath,amsfonts,amsthm} % Math packages
\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage{sectsty} % Allows customizing section commands
\allsectionsfont{\centering \normalfont\scshape} % Make all sections centered, the default font and small caps
\usepackage{fancyhdr} % Custom headers and footers
\pagestyle{fancyplain} % Makes all pages in the document conform to the custom headers and footers
\fancyhead{} % No page header - if you want one, create it in the same way as the footers below
\fancyfoot[L]{} % Empty left footer
\fancyfoot[C]{} % Empty center footer
% \fancyfoot[R]{\thepage} % Page numbering for right footer
\renewcommand{\headrulewidth}{0pt} % Remove header underlines
\renewcommand{\footrulewidth}{0pt} % Remove footer underlines
\setlength{\headheight}{13.6pt} % Customize the height of the header

\setlength\parindent{0pt} % Removes all indentation from paragraphs - comment this line for an assignment with lots of text

\usepackage[margin=0.75in]{geometry}
\usepackage{hyperref}
%----------------------------------------------------------------------------------------
%   TITLE SECTION
%----------------------------------------------------------------------------------------

\newcommand{\horrule}[1]{\rule{\linewidth}{#1}} % Create horizontal rule command with 1 argument of height

\title{ 
    \normalfont \normalsize 
    \textsc{CS 3060 Programming Languages, Fall 2022} \\ [25pt] % Your university, school and/or department name(s)
    \horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
    \huge Assignment \#1a  \\ % The assignment title
    \horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

% \author{John Smith} % Your name

% \date{\normalsize\today} % Today's date or a custom date

\begin{document}

    \begin{center}
         Homework \#1\\
        \small CS 3060 Programming Languages, Fall 2022 \\
        \small Instructor: S. Roy \\
        \huge Ruby \#1a
    \end{center}
    
    \textbf{Due Date:}  Aug 26 (11:59 pm).\\

    \textbf{Total points:} 15 points \\

    \textbf{Directions:} 
Check Gitlab \@ \texttt{https://gitlab.com/sanroy/fa22-cs3060-hw} (or check Canvas) for details. 
The prefered process for completing this assignment should be as follows:

    \begin{enumerate}[noitemsep]
        \item Fork the Repository ``fa22-cs3060-hw'' to a new Repository named ``fa22-cs3060-hw'' 
under your namespace (your gitlab username).
        \item "git clone" the newly created repository on your local machine
        \item Complete this assignment whose details are in hw1 sub-folder, committing changes to files in hw1. 
        \item Push all commits to your Gitlab repository
        \item Add TA (with his gitlab username ) and Roy (gitlab id is sanroy) as a developer of your Gitlab repository
    \end{enumerate}

If for some reason Gitlab does not work for you, then you submbit your work and README file on Canvas.

    \textbf{Tasks:}
    \begin{enumerate}[noitemsep]

         \item \textbf{(10 Points) Task \#1:} Write a C program that prints the following: 
"Hello, C is a static type language whereas Ruby is a dynamic type language". 
Use gcc command to compile the program to generate an executable file named myExe. Google a little to know
how to do it using a flag with the gcc command. Submit a screenshot showing the gcc command. 
Then, open the file myExe in pico editor and check the content of myExe. Is it readable? Submit a screenshot. 
Then, run myExe and report the outcome. Submit a screenshot showing the command. Also, submit your C program.

\item \textbf{(5 Points) Task \#2:}
Now write  a Ruby program that prints the same message as above. 
Do you need the compilation step? Also, submit your Ruby program.  
Then, run the above ruby program and report the outcome. Submit a screenshot showing the command.
What is the name of the executable file?    
\end{enumerate}
 
\end{document}
